---
title: "Assignment 2: Data transformation"
author: "Your Name"
date: "Today's date"
output: html_document
---

**Due Sunday, October 10, 2023 @ 11:59pm through Github**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(tidyverse)
load("nmes2018.rda")
```

### Question 1

* How many people in the dataset have an MSCD?

Answer:
```{r}
#Put your code for question 1 here

```

* What was the highest medical expenditure in this data?

Answer:
```{r}
#Put your code for question 1 here

```

* What was the highest medical expenditure for someone without an MSCD?

Answer:
```{r}
#Put your code for question 1 here

```

* How old is the youngest person with an MSCD?

Answer:
```{r}
#Put your code for question 1 here

```

* How old is the oldest person without an MSCD?

Answer:
```{r}
#Put your code for question 1 here

```


### Question 2
```{r}
#Put your code for question 2 here

```

### Question 3

Plot 1:
```{r}
#Put your code for plot 1 here

```

Plot 2:
```{r}
#Put your code for plot 2 here

```

Replace this text with your sentences about which plot you prefer and why.